A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-02-25 sections/Related.tex
Summary sentence
RW ITP paper

@@

\jimmy{Dunfield's new work}
DK's algorithm is shown to be sound, complete and decidable in 70 pages of manual proofs.
Though carefully written, some of the proofs are incorrect (see discussion in Section~\ref{}),
which creates difficulties when formalizing them in a proof assistant.
Their follow-up work~\cite{} enriches the bidirectional higher-rank system with
existentials and indexed types.
With a more complex declarative system, they developed a proof of over 150 pages.
It is even more difficult to argue its correctness for every single detail within such a big development.
Unfortunately, we find that their Lemma 26 (Parallel Admissibility) appears to have the same issue 
as lemma 29 discussed in Section~\ref{}: the conclusion is false.
\bruno{I think you will need to justify this better and in the appendix you must show
the lemma and counter-example.}
\bruno{Missing Simon Peyton Jones work: which is the other predicative work.
  Maybe the OutsideIn work can also be briefly mentioned (you can ask Tom for details
  of that work).
 }

@@

\paragraph{Mechanical Formalization of Polymorphic Subtyping}
In all previous work on type inference for higher-ranked polymorphism
(predicative and impredicative) discussed above, all proofs and
metatheory are manual. The only partial effort on mechanizing aspects of type inference
for higher-ranked types is
the Abella formalization of \emph{polymorphic subtyping} by
\citet{itp2018}. ... \bruno{a comparison with our own ITP paper here!}

>>>>

Throughout the paper we have already discussed much of the closest related work.
In this section we summarize the key differences and novelties, and we discuss some other
related work.

@@

\jimmy{Dunfield's new work}
DK's algorithm is shown to be sound, complete and decidable in 70 pages of manual proofs.
Though carefully written, some of the proofs are incorrect (see discussion in Appendix),
which creates difficulties when formalizing them in a proof assistant.
Their follow-up work~\cite{} enriches the bidirectional higher-rank system with
existentials and indexed types.
With a more complex declarative system, they developed a proof of over 150 pages.
It is even more difficult to argue its correctness for every single detail within such a big development.
Unfortunately, we find that their Lemma 26 (Parallel Admissibility) appears to have the same issue 
as lemma 29 discussed in Appendix: the conclusion is false.
\bruno{I think you will need to justify this better and in the appendix you must show
the lemma and counter-example.}
\bruno{Missing Simon Peyton Jones work: which is the other predicative work.
  Maybe the OutsideIn work can also be briefly mentioned (you can ask Tom for details
  of that work).
 }

@@

\paragraph{Mechanical Formalization of Polymorphic Subtyping}
In all previous work on type inference for higher-ranked polymorphism
(predicative and impredicative) discussed above, all proofs and
metatheory are manual. The only partial effort on mechanizing aspects of type inference
for higher-ranked types is
the Abella formalization of \emph{polymorphic subtyping} by \citet{itp2018}.
The judgment form of worklist $\Gm \vdash \Omega$ used in the formalization simplifies
the propagation of existential variable instantiations.
However, the approach has two main drawbacks;
it does not collect unused variable declarations effectively,
and the simple form of judgment cannot handle inference modes, which outputs types.
The new worklist introduced in this paper inherits the simplicity of propagating instantiations,
but overcome both of the issues by mixing judgments with declarations
and using the continuation-passing-style judgment chains.
\bruno{a comparison with our own ITP paper here!}
